Title

### 2013-03-24 inc/design_considerations/considerations.tex
clean up the introductions to the hardware and consideration sections
began section on transverse emittance limitations

%Ultrafast Electron Microscopy (UEM) is a subclass of a more general concept, Dynamic Transmission Electron Microscopy (DTEM).
%DTEM is a more general term for any electron microscope with higher time resolution, typically employing laser-stimulated photoemission.

@@

\section{Generation Current Limitations}

@@

>>>>

@@

\section{Generation Current Limitations} \label{sec:childs_law}

@@

A common figure of merit for electron beams is its normalized transverse emittance \cite{jensen_emittance_2010}, $\varepsilon_{\smallT}$, defined as 
\begin{equation} \label{eq:emittance_definition}
  \varepsilon_{\smallT} = \frac{1}{m c} \sqrt{ \left < x^2 \right > \left < p_x^2 \right > } \,\text{,}
\end{equation}
where $m$ is the electron mass, $c$ is the speed of light in vacuum and $x$ and $p_x$ are the transverse position and momentum respectively.
By Liouville's Theorem (Section \ref{sec:liouville}), we know that this quantity is conserved throught the propagation of the pulse, and therefore is related directly to the initial photoemission properties of the system.
For a laser of the form of \ref{eq:laser_form} we have simply
\begin{equation} \label{eq:emittance_definition_w}
  \varepsilon_{\smallT} = \frac{w}{m c} \sqrt{ \left < p_x^2 \right > } \,\text{.}
\end{equation}

This normalized transverse emittance limits the resolving capablility of the beam, so this quantity can be thought of as a measure of the beam quality, where a lower number is preferred.
In Ref. \ref{berger_dc_2009}, we explore these limitations, eventually arriving at the following result.
For a desired spatial resolution per pixel $\Delta X$ (related to the magnification) using a $N_p$ x $N_p$ detector, in the M$^{th}$ diffraction order, one may only resolve dynamics arising from a diffraction peak shift $\Delta a / a$ where the Bragg plane spacing is $a$ if 
\begin{equation}
  \varepsilon_{\smallT} \le \frac{5 \hbar}{m c} N_p \, \Delta X \frac{M}{a} \left ( \frac{\Delta a}{a} \right ) \,\text{.}
\end{equation}
